### 2016-08-28 ReviewComments/response.tex

\documentclass{vldb}
\usepackage{url}
\newcounter{ctResp}
\newcommand{\response}[1]{
\addtocounter{ctResp}{1}
\textbf{Response \arabic{ctResp}:} #1 \\}

\begin{document}
\title{Response to reviewers' comments for Paper \# 278}
\maketitle

We are deeply grateful to all the reviewers for the generous and insightful
suggestions which help us to improve this work to a better level.
In the following, we provide explicit response to each raised concern and address our corresponding revisions in the new submission.

### 2016-08-28 ReviewComments/review1.tex
New revision
...

\response{We agree that utilizing advanced Spark features would 
improve our solutions. In this work, we do not include 
these optimization in-depth because we set out focus 
on solving the challenges in parallelizing the 
GCMP mining algorithms.
We are also in progress of open-sourcing a Spark-tailored
version of SPARE.
}

>>>>

\response{
We agree with the reviewer that utilizing advanced Spark features
would benefit our solutions. In fact, our SPARE algorithm has already taken advantages of the Spark-only features (i.e., caching of RDDs and DAG execution engine). As described in Section 5.3, our SPARE algorithm uses a run-time best-fit strategy to achieve load balance. Using the DAG execution engine, we are able to adopt a Map-Planning-Reduce work flow. With the support of in-memory caching of RDDs,
the Map results need not to be recomputed after the planning phase. As the result shown in Figure 8,  SPARE with best-fit strategy saves 15\% total time as compared to the randomly partition strategy (i.e., SPARE-RD).  If without Spark's features, such an optimization would be hardly possible.

We do not consider utilizing other Spark extensions such as Spark-GraphX, Spark-Streaming and Spark-MLlib because these extensions, as their name suggest, are for different application scenarios.
%
%We are unsure about whether adapting other features in Spark (e.g., Spark streaming, Spark SQL, Spark Graph) would help to improve our solutions. Since they are solutions 
%%
%
%In this work, we do not include 
%these optimization in-depth because we set out focus 
%on solving the challenges in parallelizing the 
%GCMP mining algorithms.
%We are also in progress of open-sourcing a Spark-tailored
%version of SPARE.
}

### 2016-08-28 ReviewComments/review2.tex
New revision
...

\response{
We agree the fact that the gap parameter is an old concept. Nevertheless, our major contribution in
modeling lies in unifying existing movement patterns in the trajectory domain. 
The gap parameter is naturally introduced to 
solve the loose-connection anomaly (as in Figure 2).
%which is suffered by the state-of-the-art generalization (i.e., Platoon pattern). 
In the revision, we add Section 2.5 to accredit the origin of the \emph{gap} concept
and distinguish the sequential mining problem with our problem. 
}

>>>>

\response{We agree with the reviewer that the gap parameter is an old concept. However, we use the gap parameter merely for solve the loose-connection anomaly (as in Figure 2).

However, our major contribution in modeling of GCMP is not on the gap parameter and our problem is very different from the sequence mining problem.

We agree the fact that the gap parameter is an old concept. Nevertheless, our major contribution in
modeling lies in unifying existing movement patterns in the trajectory domain. 
The gap parameter is naturally introduced to 
solve the loose-connection anomaly (as in Figure 2).
%which is suffered by the state-of-the-art generalization (i.e., Platoon pattern). 
In the revision, we add Section 2.5 to accredit the origin of the \emph{gap} concept
and distinguish the sequential mining problem with our problem. 
}
